% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
\usepackage{enumitem}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Manas Pande}  & 519-781-4944\\
34 Columbia Street West &  mpande@uwaterloo.ca \\
Waterloo, ON N2L 3K5 & http://www.manaspande.com\\ 
& https://github.com/mpande1998\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Personal Projects}
\begin{itemize}
\item
	\ressubheading{Indian Railways Application}{\textit{In Development}}{GitHub: https://goo.gl/Hjlrl3}{}
	\begin{itemize}
		\resitem{Android application that lets users get live information about their ticket, train status, seat availability, and more.}
		\resitem{Used OkHttp to make network requests to a REST API.}
		\resitem{Implemented train name, number and station code auto-complete; the app sends requests to a REST API with the partial user input and displays matching results.}
		\resitem{Adhered to the Material Design guidelines:
		\begin{itemize}[label={--}]
			\resitem{Used CoordinatorLayout, Material theme, and Roboto.}
			\resitem{Applied custom animations -- touch feedback, activity transitions.}
		\end{itemize}}
		\resitem{See demo on Vimeo: https://goo.gl/nMIo4l}
	\end{itemize}

\item
	\ressubheading{Find Blood Banks India}{\textit{December 2016}}{GitHub: https://goo.gl/L0l9Ki}{}
	\begin{itemize}
		\resitem{Android application that lets users find blood banks by state and district.}
		\resitem{Contains data for 2900+ blood banks; provides address, contact information, and more.}
		\resitem{Created an SQLite database with the information, and made an application that queries data from that database.}
		\resitem{Used ExpandableRecyclerView to display the results, making the UI compact.}
		\resitem{See demo on YouTube: https://goo.gl/MNNNeq}
	\end{itemize}

\item
	\ressubheading{Personal Website}{\textit{December 2016}}{GitHub: https://goo.gl/QRu6Tn}{}
	\begin{itemize}
		\resitem{Personal website in HTML, CSS, and Javascript with links to my GitHub, e-mail, and resume.}
		\resitem{Made the website responsive using CSS Flexbox, and ensured that it is mobile-friendly.}
	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Java, Python, HTML, CSS, JavaScript, Racket
\item[Libraries/Frameworks:]
jQuery, OkHttp, ButterKnife, Volley, BootStrap
\item[Technologies:]
Git, Android Studio, MySQL, \LaTeX
\item[Concepts:]
Mobile UI/UX, REST APIs, OOP, JSON, Networking, Databases
\end{description}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{University of Waterloo}{Waterloo, ON}{B.A.Sc., Computer Science, Co-op}{Class of 2021}

\end{itemize}

\end{document}
